Theory of Phonon Polaritons in Polar Dielectrics

### 2018-08-05 paper.tex
added an acknowledgements sectiokn

>>>>

\section{Acknowledgements}
This research used resources of the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science
of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231.
NR and JC recognize the support of the DOE Computational Science Graduate Fellowship (CSGF). PN acknowledges start-up funding from the Harvard John A. Paulson School of Engineering and Applied Sciences. %The authors thank XXXX for helpful discussions.
